|

### 2025-05-25 doc/paper.qmd
png adapted

The results are further contrasted with Gapminder’s interactive global development visualizations as of 2021 [@gapminder_health_chart]. This comparative discussion is provided in @sec-task2. The project concludes with reflections on transparency, reproducibility, and the importance of making research accessible to a broader audience, as discussed in @sec-conclusion.

>>>>

The results are further contrasted with Gapminder’s interactive global development visualizations as of 2021 [@gapminder_health_chart]. This comparative discussion is provided in @sec-task2. The project concludes with reflections on transparency, reproducibility, and importance of making research accessible to a broader audience, as discussed in @sec-conclusion.
